---
title: "BRE daily report"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output: 
  flexdashboard::flex_dashboard:
    orientation: columns
    vertical_layout: fill
    theme: lumen 
---

<style>

.navbar-brand {
  display: grid;
  margin: auto;
  padding: 5px;
}

.navbar-author {
  margin-left: 0px;
}
</style>

```{r setup, include=FALSE}

#-----------------------------------------------------------------------
## FILE        : UI.R - USER INTERFACE             DATE : 19/08/2020
##
## CREATED BY  : Joshua Allen
##
## DESCRIPTION : daily report for monitoring account A benchmark activity: 
##               including nostro balances, 
##               repo specials, 
##               short covers 
##


# source environment files
source("\\\\istdba/BuildArchive/ShinyApps/EnvironmentScript/EnvironmentScript_Latest/LOCAL/Artifactory/environment.R")

# boe checkpoint
checkpoint_date <- "2022-01-01"
message(paste0("checkpoint_date: ", checkpoint_date))
boeCheckpoint(checkpoint_date, scanForPackages = FALSE)

# load packages -----------------------------------------------------


library(DT)
library(dplyr)
library(formattable)
library(flexdashboard)
library(httr)
library(lubridate)
library(purrr)
library(plotly)
library(Rblpapi)
library(scales)
library(stringr)
library(zoo)

# Load a library so that boeCheckpoint won't complain about it being missing
FIRVr_str <- "library(FIRVr, lib.loc = 'N:/Offdata/RM/_R code repository/RMPackages/_R4.0')"
eval(parse(text=FIRVr_str))

options(digits = 2)
options(DT.fillContainer = T)
options(scipen = 999)

# source functions ---------------------------------------------------------

source(file.path("../functions/functions.R"))
source(file.path("../functions/openlink_api.R"))


# set parameters -------------------------------------------------------
currencies <- c("CAD", "AUD", "USD", "EUR", "JPY")
date <- Sys.Date()
folder_date <- format(date, "%y%b%d")
file_date <- format(date, "%d-%b-%y")
ex_day <- 0
lightgreen <- "#d5f7d5"
lightred <- "#f7d7d5"

openlink_data_path <- file.path("G:", "DB_Data", "OLFLIVE", "outdir", "Daily_Pnl_Reports")
nostro_report <- file.path("G:/DB_Data/OLFLIVE/outdir/reports", folder_date, "RTPE_Cash_By_Nostro_Export.csv")

# source modules for report ----------------------------------------------
source("../modules/get_data.R")
source("../modules/repo_shorts.R")
source("../modules/repo_covers.R")
source("../modules/fx_swaps.R")
```

<script>
$(document).ready(function(){
    $('[data-toggle="popover"]').popover(); 
});
</script>

Nostro Accounts {data-icon="fa-receipt"}
=====================================  

Column {data-width=75}
-------------------------------------

### Nostro breaks 

```{r NOSTRO_BREAK, results='asis', echo = FALSE}

if (length(nostro_errors) < 1) {
  cat(sprintf(
    "<span style = \"color: %s;\">%s</span>\n\n",
    "green",
    paste0("There are no nostro breaks in the next 10 business days")
  ))
} else {
  cat(sprintf(
    "<span style = \"color: %s;\">%s</span>\n\n",
    "red",
    paste0(
      "There is ",
      length(nostro_errors),
      " breaks to check in the next 10 business days for the following currencies: ",
      paste0(unique(errors$Currency), collapse = ", ")
    ), 
    "."
  ))
}

```

### Nostro warnings 

```{r NOSTRO_WARN, results='asis', echo = FALSE}

if (length(nostro_warnings) < 1) {
  cat(sprintf(
    "<span style = \"color: %s;\">%s</span>\n\n",
    "green",
    paste0("There are no nostro warnings (within 10% of min/max limit) in the next 10 business days")
  ))
} else {
  cat(sprintf(
    "<span style = \"color: %s;\">%s</span>\n\n",
    "red",
    paste0(
      "There are ",
      length(nostro_warnings),
      " to check for the following currencies: ",
      paste0(unique(warnings$Currency), collapse = ", "),
      "."
    )
  ))
}



```

### Repo shorts 

```{r SHORT_WARN, results='asis', echo = FALSE}

if (length(shorts) < 1) {
  cat(sprintf(
    "<span style = \"color: %s;\">%s</span>\n\n",
    "green",
    paste0("There are no repo shorts to cover in the next 10 business days")
  ))
} else {
  cat(sprintf(
    "<span style = \"color: %s;\">%s</span>\n\n",
    "red",
    paste0(
      "There are ",
      nrow(shorts),
      " repo short covers in the next 10 business days for the following currency portfolios: ",
      paste0(unique(shorts$CURRENCY), collapse = ", "),
      ".", 
      " The first is out of ", paste0(shorts$T_PLUS[1]), 
      "."
    )
  ))
}



```

### Repo specials 

```{r SPECIAL_WARN, results='asis', echo = FALSE}

if (length(specials) < 1) {
  cat(sprintf(
    "<span style = \"color: %s;\">%s</span>\n\n",
    "green",
    paste0("There are no repo specials rolling off in the next 10 business days")
  ))
} else {
  cat(sprintf(
    "<span style = \"color: %s;\">%s</span>\n\n",
    "red",
    paste0(
      "There are ",
      length(unique(specials$TICKER)),
      " repo specials rolling off in the next 10 business days for the following currency portfolios: ",
      paste0(unique(specials$CURRENCY), collapse = ", "),
      "."
    )
  ))
}



```


Column {.tabset}
-------------------------------------

### Nostro (total balances)

```{r NOSTRO_TOTAL,  results='asis',  out.height= "85%"}

ism <- nostro_dt %>% lapply(class) %>% unlist == "numeric"
chr <- nostro_dt %>% lapply(class) %>% unlist == "character"

df <-  dplyr::filter(nostro_dt, account == "Total")

DT::datatable(
  df,
   extensions = c("RowGroup", "Buttons", "Scroller"),
  options = list(pageLength = 20,
                 dom = 't'),
  rownames = FALSE, 
  selection = "none"
) %>%
  formatStyle(chr,
              fontWeight = "bold") %>%
  formatStyle(ism, color = styleInterval(0, c("red", "black"))) %>%
  formatStyle(ism, backgroundColor = styleInterval(0, c(lightred, lightgreen))) %>%
  formatStyle("WithinLimit",
              fontWeight = "bold",
              color = styleEqual(c("Yes", "No"), c("green", "red"))) %>%
  formatCurrency(ism ,
                 currency = "",
                 interval = 3,
                 mark = ",")  %>%
  formatRound(ism, digits = 0)

```


### Nostro (all accounts)

```{r NOSTRO_ALL}


ism <- nostro_dt %>% lapply(class) %>% unlist == "numeric"
chr <- nostro_dt %>% lapply(class) %>% unlist == "character"

DT:: datatable(
  nostro_dt,
  extensions = c("RowGroup", "Buttons", "Scroller"),
  rownames = FALSE,
  filter = "top", 
  escape = FALSE,
  selection = "none",
  options = list(
    pageLength = 20,
    selection = "none",
    rowGroup = list(
      dataSrc = 0
    ),
    fnDrawCallback = htmlwidgets::JS(
      "function() { HTMLWidgets.staticRender(); }"
    )
  )
) %>% 
  formatStyle(
    chr,
    fontWeight = "bold"
  ) %>% 
  formatStyle(ism, color = styleInterval(0, c("red", "black"))) %>%
  formatStyle(ism, backgroundColor = styleInterval(0, c(lightred, lightgreen))) %>%
  formatStyle("WithinLimit",
              fontWeight = "bold",
              color = styleEqual(c("Yes", "No"), c("green", "red")))



```


Repo Specials {data-icon="fa-shopping-cart"}
=====================================  

Column {data-width=50}
-------------------------------------

### List of existing specials

```{r, results='asis', echo = FALSE}

RSGC <- OL_specials %>% 
  dplyr::ungroup() %>% 
  dplyr::select(TICKER, CURRENCY) %>%
  dplyr::mutate(instruments =  gsub(pattern = "_", " ", TICKER), 
                issuer_coupon = gsub('.{6}$', '', instruments), 
                date = stringr:: str_sub(instruments, - 6, - 1), 
                day = stringr:: str_sub(date, 1, 2),
                month = stringr:: str_sub(date, 3, 4), 
                year = stringr:: str_sub(date, 5, 6), 
                date = paste0(month, "/", day, "/", year)
                ) %>% 
  dplyr::mutate(SECURITY = paste0(issuer_coupon, date)) %>% 
  dplyr::select(SECURITY, CURRENCY) %>% 
  dplyr::arrange(CURRENCY)


cat(sprintf(
  "<span style = \"color: %s;\">%s</span>\n\n",
  "#00008b",
  paste0(unique(RSGC$SECURITY), collapse = " <br> ")
))



```


Column {.tabset}
-------------------------------------

### Repo Specials (by Currency)

```{r RSGC_CURRENCY,  results='asis',  out.height= "85%"}

x <- specials
final_col <- rep(FALSE, ncol(x))
final_col[[length(final_col)]] <- TRUE

datatable(
  x,
  extensions = c("RowGroup", "Buttons", "Scroller"), 
  rownames = FALSE,
  filter = "top", 
  options = list(
    rowGroup = list(
      dataSrc = 0
    ),
    pageLength = nrow(x),
    paging = FALSE, 
    ordering = FALSE,
    lengthChange = FALSE,
    searching = FALSE,
    info = FALSE
  )
) %>% 
  formatStyle("Change on day", color = styleInterval(0, c("red", "black"))) %>% 
  formatStyle("POSITION", color = styleInterval(0, c("red", "black")))   %>% 
  formatStyle(final_col, backgroundColor = lightgreen)

```

### Repo Specials (by Security)

```{r RSGC_SECURITY,  results='asis',  out.height= "85%"}

x <- specials
final_col <- rep(FALSE, ncol(x))
final_col[[length(final_col)]] <- TRUE

datatable(
  x,
  extensions = c("RowGroup", "Buttons", "Scroller"), 
  rownames = FALSE,
  filter = "top", 
  options = list(
    rowGroup = list(
      dataSrc = 1
    ),
    pageLength = nrow(x),
    paging = FALSE, 
    ordering = FALSE,
    lengthChange = FALSE,
    searching = FALSE,
    info = FALSE
  )
) %>% 
  formatStyle("Change on day", color = styleInterval(0, c("red", "black"))) %>% 
  formatStyle("POSITION", color = styleInterval(0, c("red", "black")))  %>% 
  formatStyle(final_col, backgroundColor = lightgreen)

```


Repo Short Covers {data-icon="fa-umbrella"}
=====================================  

Column {data-width=1200}
-------------------------------------

### Upcoming shorts to cover (up to T + 10)

```{r SHORT_COVERS,  results='asis',  out.height= "85%"}

x <- shorts
final_col <- rep(FALSE, ncol(x))
final_col[[length(final_col)]] <- TRUE

datatable(
  x,
  extensions = c("RowGroup", "Buttons", "Scroller"), 
  rownames = FALSE,
  filter = "top", 
  options = list(
    rowGroup = list(
      dataSrc = 0
    ),
    pageLength = nrow(x),
    paging = FALSE, 
    ordering = FALSE,
    lengthChange = FALSE,
    searching = FALSE,
    info = FALSE
  )
) %>% 
  formatStyle(final_col, color = styleInterval(0, c("red", "black"))) %>% 
  formatStyle(final_col, backgroundColor = lightgreen)

```

FX swaps {data-icon="fa-receipt"}
=====================================  

Column {data-width=300}
-------------------------------------


### Funding out of USD 

```{r FX_USD,  results='asis',  out.height= "85%"}

plot_data <- dplyr::filter(fx_swap_returns, base == "USD")
plot_term_structure(plot_data, xlab = "maturity", ylab = "total_return", fill = "currency", polynomial_order = 3)

```

### FX swap table (USD)

```{r FX_USD_DT,  results='asis',  out.height= "100%"}

make_fx_datatable(dplyr::filter(fx_dt, base == "USD"))

```




Column {data-width=300}
-------------------------------------

### Funding out of EUR 

```{r FX_EUR,  results='asis',  out.height= "85%"}

plot_data <- dplyr::filter(fx_swap_returns, base == "EUR")
plot_term_structure(plot_data, xlab = "maturity", ylab = "total_return", fill = "currency", polynomial_order = 3)

```


### FX swap table (EUR)

```{r FX_EUR_DT,  results='asis',  out.height= "100%"}

make_fx_datatable(dplyr::filter(fx_dt, base == "EUR"))

```


Column {data-width=300}
-------------------------------------

### Funding out of CAD 

```{r FX_cAD,  results='asis',  out.height= "85%"}

plot_data <- dplyr::filter(fx_swap_returns, base == "CAD")
plot_term_structure(plot_data, xlab = "maturity", ylab = "total_return", fill = "currency", polynomial_order = 3)

```


### FX swap table (CAD)

```{r FX_CAD_DT,  results='asis',  out.height= "100%"}

make_fx_datatable(dplyr::filter(fx_dt, base == "CAD"))

```

